---
title: "F0, Duration Table"
output:
  distill::distill_article:
    self_contained: yes
    mode: selfcontained
---

<style>
.tooltip {
  position: relative;
  display: inline-block;
}

.tooltip .tooltiptext {
  visibility: hidden;
  width: 120px;
  background-color: black;
  color: #fff;
  text-align: center;
  padding: 5px 0;
  border-radius: 6px;
 
  position: absolute;
  z-index: 1;
  bottom: 100%;
  left: 50%;
  margin-left: -60px;
}

.tooltip:hover .tooltiptext {
  visibility: visible;
}

.ReactTable .rt-table {
  overflow: visible;
}

</style>

### Keys

- **Bar length** corresponds to <span style='font-variant: small-caps;'>Duration</span>, and reflects the _absolute_ durations of words/pauses. Bar length is normalized w.r.t. the longest reported duration in the data for an element, which is ~ 2,450ms long: <span style='margin-left:10px; border: 1px solid black; font-size: 3px; background-color: lightgrey; vertical-align: middle; padding-right: 150px'></span>

- **Bar color** corresponds to <span style='font-variant: small-caps;'>Mean F0</span> and reflects the _relative_ mean F0 of words compared to other in the _same sentence_. The following diverging color palette is used to mark relative mean F0, where blue hues are below average and red hues are above average.

```{r, out.width = '500px', out.height = '25px', out.extra= 'style = "display: block; margin: auto;"'}
chroma::show_col(colorspace::diverge_hcl(7, palette = 'Blue-Red 2'))
```

- **Silence** (sp) is marked with the unicode character &#9676;

```{r tbl-code, echo = FALSE, message = FALSE, layout = 'l-screen'}
library(dplyr)
library(readr)
library(scales)
library(colorspace)
library(stringr)
library(glue)
library(reactable)

# Read in and process data
data_raw <- read_csv("C:/Users/jchoe/Downloads/may_fixed_encoding.txt")
df <- data_raw %>% 
  mutate(
    Duration = abs(Duration),
    across(contains("F0"), ~ as.numeric(replace(.x, which(.x == "--undefined--"), NA))),
    across(c(Passage, Sentence, MeasurementOrder), as.integer),
    across(contains("F0"), ~ replace(.x, which(data_raw$MeasurementLabel == "sp"), NA))
  ) %>% 
  select(-Speaker)


# Helper function
html_word_bar <- function(word, fill, color, padding, size, margin, tooltip, border_style) {
  stringr::str_squish(glue::glue("
    <div style='float: left; text-align: center'>
      <div class='tooltip'>
        <span style='margin: {margin}px; background-color: {fill};\\
          border: 1px {border_style} black; padding-left: {padding}px;\\
          padding-right: {padding}px; font-size: {size}px'></span>
        <span class='tooltiptext'>{tooltip}</span>
      </div>
      <br>
      <span style='margin: {margin}px; color: {color}'>{word}</span>
    </div>
  "))
}

# Add styles
df_combined <- df %>% 
  group_by(Passage, Sentence) %>% 
  filter(!(MeasurementOrder %in% range(MeasurementOrder) & MeasurementLabel == "sp")) %>% 
  ungroup() %>% 
  mutate(
    dur_scaled = (Duration - min(Duration))/diff(range(Duration)),
    padding = round(dur_scaled * 150 / 2, 1),
    word = replace(MeasurementLabel, MeasurementLabel == "sp", "&#9676;")
  ) %>% 
  group_by(Passage, Sentence) %>% 
  mutate(
    fill = scales::col_numeric(
      palette = colorspace::diverge_hcl(7, palette = 'Blue-Red 2'),
      na.color = "white",
      domain = MeanF0
    )(MeanF0),
    color = "black"
  ) %>% 
  ungroup() %>% 
  mutate(
    border_style = ifelse(MeasurementLabel == "sp", "dotted", "solid"),
    tooltip = glue("{round(Duration, 3) * 1000}ms{ifelse(!is.na(MeanF0), paste0(', ', round(MeanF0), 'Hz'), '')}"),
    html = html_word_bar(word, fill, color, padding, size = 3, margin = 5, tooltip, border_style)
  )

# Add tooltip and collapse
df_tbl_combined <- df_combined %>% 
  group_by(Passage, Sentence) %>% 
  summarize(
    Label = stringr::str_squish(paste(html, collapse = "")),
    .groups = 'drop'
  )

# Render Table
df_tbl_combined %>%
  reactable(
    groupBy = "Passage",
    searchable = TRUE,
    pagination = TRUE,
    columns = list(
      Passage = colDef(width = 100),
      Sentence = colDef(width = 100),
      Label = colDef(
        html = TRUE,
        style = list(overflow = "visible"), 
        resizable = TRUE
      )
    ),
    style = list(
      margin = "100px"
    )
  )
  
```

<br>

## Code

```{r eval = FALSE, echo = TRUE}
<<tbl-code>>
```
